---
title: "Jedi Darkness Analysis"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{jedi_analysis}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
```

## Load packages and data

```{r load}
library(jediAnalysis)
require(lme4)
require(flexplot)
d = jedi
```

## Baseline model

Intercept-only model to estimate ICC — how much of the variation in darkness is due to dojo differences.

```{r baseline}
baseline = lmer(darkness ~ 1 + (1 | dojo_id), data = d)
summary(baseline)
```

## Fixed anger effect

Add anger as a fixed effect to test whether anger predicts darkness across all dojos.

```{r fixed_anger}
fixed_anger = lmer(darkness ~ 1 + anger + (1 | dojo_id), data = d)
summary(fixed_anger)
```

## Random + fixed anger effect

Allow the effect of anger to vary across dojos (random slope).

```{r fixed_random_anger}
fixed_random_anger = lmer(darkness ~ 1 + anger + (1 + anger | dojo_id), data = d)
summary(fixed_random_anger)
```

## Main model: does emotional attachment increase darkness, controlling for anger?

```{r main_model}
model = lmer(darkness ~ anger + emotional_bonds +
               (anger + emotional_bonds | dojo_id), data = d,
             control = lmerControl(optimizer = "bobyqa"))
summary(model)
estimates(model)
```

## Visualise model predictions (overall)

Shows the overall model-predicted relationship between predictors and darkness.

```{r plot_overall}
visualize(model, plot = "model")
```

## Visualise emotional bonds effect by anger level

Shows how emotional_bonds predicts darkness at different levels of anger, across dojos.

```{r plot_eb_anger}
visualize(model, plot = "model",
          formula = darkness ~ emotional_bonds + dojo_id | anger)
```

## Visualise emotional bonds across 30 sampled dojos

Plots the emotional_bonds effect for a random sample of 30 dojos to avoid overplotting.

```{r plot_eb_dojos}
visualize(model, plot = "model",
          formula = darkness ~ emotional_bonds + dojo_id, sample = 30)
```

## Visualise anger across 30 sampled dojos

Plots the anger effect for a random sample of 30 dojos.

```{r plot_anger_dojos}
visualize(model, plot = "model",
          formula = darkness ~ anger + dojo_id, sample = 30)
```

## Model comparison: is the random slope for anger necessary?

Compare full model (random slopes for both) vs reduced model (random slope for emotional_bonds only).

```{r model_comparison}
reduced = lmer(darkness ~ emotional_bonds + anger + 
                 (emotional_bonds | dojo_id), data = d,
               control = lmerControl(optimizer = "bobyqa"))
compare.fits(darkness ~ anger | emotional_bonds + dojo_id, 
             data = d, model1 = model, model2 = reduced, re = T)
model.comparison(model, reduced)
```

## Residual diagnostics

Check model assumptions — residuals should be roughly normal and show no patterns.

```{r residuals}
visualize(model, plot = "residuals")
```
